Constant Partying: \\ Introducing a Generic Toolkit for Recursive Partitioning in R

### 2014-02-11 pkg/partykit/inst/NUS-2014/constparty_TH_AZ.Rnw
cosmetics; mostly
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@457 255f4249-2263-4417-b1ea-8498779e27a7

<<data>>=
data("Titanic", package = "datasets")
ttnc <- as.data.frame(Titanic)
ttnc <- ttnc[rep(1:nrow(ttnc), ttnc$Freq), 1:4]
names(ttnc)[2] <- "Gender"
ttnc <- transform(ttnc, Treatment = factor(
  Gender == "Female" | Age == "Child",
  levels = c(FALSE, TRUE),
  labels = c("Normal\n(Male&Adult)", "Preferential\n(Female|Child)")
))
@

@@

<<evtree, eval=FALSE>>=
set.seed(1071)
ev <- evtree(Survived ~ Gender + Age + Class, 
             data = ttnc, maxdepth = 3)
@

@@

\title[Constant Partying]{Constant Partying: \\ 
      Introducing a Generic Toolkit for Recursive Partitioning in R}
\author{Torsten Hothorn (Universit\"at Z\"urich) \\
        Achim Zeileis (Universit\"at Innsbruck)}
%\URL{http://user.math.uzh.ch/hothorn/}
%\lecture{partykit: A Toolkit for Recursive Partytioning}

@@

\textbf{Intention:}
\begin{itemize}
  \item Illustrate several trees using the same data.
  \item Not use the iris data (or something from mlbench).
\end{itemize}

\textbf{Solution:}
\begin{itemize}
  \item Use Titanic survival data (oh well\dots).
  \item In case you are not familiar with it: Survival status, gender, age (child/adult), and
    class (1st, 2nd, 3rd, crew) for the \Sexpr{nrow(ttnc)}~persons on the ill-fated
    maiden voyage of the Titanic.
\end{itemize}

@@

\setkeys{Gin}{width=1.1\textwidth}
\hspace*{-0.4cm}%
<<Titanic-pmml-visualization, fig=TRUE, height=8, width=12>>=
plot(pm)
@

@@

@@

Hothorn T, Zeileis A (2013).
 \textit{partykit: A Toolkit for Recursive Partytioning.}
 R~package vignette version~0.1-6.
 URL~\url{http://CRAN.R-project.org/package=partykit}

>>>>

<<data>>=
data("Titanic", package = "datasets")
ttnc <- as.data.frame(Titanic)
ttnc <- ttnc[rep(1:nrow(ttnc), ttnc$Freq), 1:4]
names(ttnc)[2] <- "Gender"
ttnc <- transform(ttnc, Treatment = factor(
  Gender == "Female" | Age == "Child",
  levels = c(FALSE, TRUE),
  labels = c("Normal\n(Male&Adult)", "Preferential\n(Female|Child)")
))
set.seed(1071)
@

@@

<<evtree, eval=FALSE>>=
ev <- evtree(Survived ~ Gender + Age + Class, 
             data = ttnc, maxdepth = 3)
@

@@

\title[Constant Partying]{Constant Partying: \\ 
      Introducing a Generic Toolkit for Recursive Partitioning in R}
\author{Torsten Hothorn (Universit\"at Z\"urich) \\
        Achim Zeileis (Universit\"at Innsbruck)}
\date{NUS 2014}
%\URL{http://user.math.uzh.ch/hothorn/}
%\lecture{partykit: A Toolkit for Recursive Partytioning}

@@

\textbf{Intention:}
\begin{itemize}
  \item Illustrate several trees using the same data.
  \item Here: Titanic survival data.
  \item In case you are not familiar with it: Survival status, gender, age (child/adult), and
    class (1st, 2nd, 3rd, crew) for the \Sexpr{nrow(ttnc)}~persons on the ill-fated
    maiden voyage of the Titanic.
\end{itemize}

@@

\setkeys{Gin}{width=1.1\textwidth}
\hspace*{-0.4cm}%
<<Titanic-pmml-visualization, fig=TRUE, height=10, width=16>>=
plot(pm)
@

@@

\begin{frame}
\frametitle{findsplit}

R code

\begin{frame}
\frametitle{growtree}

R code

\begin{frame}[fragile]
\frametitle{mytree}

R code

<<Titanic-mytree-vis, eval = FALSE, echo = TRUE>>=
plot(mytree(Survived ~ Class + Age + Gender, 
            data = ttnc))
@

@@

Hothorn T, Zeileis A (2014).
 \textit{partykit: A Toolkit for Recursive Partytioning.}
 R~package vignette version~0.2-0.
 URL~\url{http://CRAN.R-project.org/package=partykit}
